\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\graphicspath{  {./Figures/}  } 
\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}

% ========== Title Page ==========
\title{Heat Exchanger}
\author{
	\textbf{Submitted by}: \\
	Henry V. Gilbert \\
	The University of Tennessee Knoxville \\
	hgilber1@vols.utk.edu \\
	(931) - 335 - 0669 \\
	960 Riverside Forest Way
	Apt. 002 \\
	Knoxville TN, 37915\\ \\ \\ \\ \\ \\ \\ 
	\textbf{Submitted to: }\\ 
	Dr. Seyedreza Djeddi \\
	Research Assistant Professor and Lecturer \\
	Tickle College of Engineering, MABE Department \\
	314 Perkins Hall \\
	1506 Middle Drive \\
	Knoxville TN, 37996 \\
	}
\date {March 26 2019}
\begin{document}
\pagenumbering{gobble}
\maketitle

% ================.Letter of Transmittal   ====================
\newpage
\section*{Letter of Transmittal}
Dr. Seyedreza Djeddi \\
Research Assistant Professor and Lecturer \\
Tickle College of Engineering, MABE Department \\
314 Perkins Hall \\
1506 Middle Drive \\
Knoxville TN, 37996 \\ \\
Dear Dr. Djeddi: \\ 

In this packet I am submitting a formal lab report for the thin walled pressure vessel experiment, 
conducted under your supervision. This experiment studied the relationship between stress and
strain using a thin walled pressure vessel. Based on theoretical equations, the hoop and 
axial stress can be determined knowing the pressure vessel radius, wall thickness, and internal
pressure. Experimentally, one can determine the internal stresses using strain transformations,
principal strains, and Hooke's law. The acquired strain data allowed us to determine that Rosettes A 
and B were the least accurate, and Rosettes C and D were highly accurate in measuring 
principal stresses. The data analysis involved comparing measured normalized strain relationships,
measured principal stresses to theoretical principal stresses, and measured hoop stress to 
measured axial stress. Most of the data followed a linear trend, so the inconsistencies in Rosettes A 
and B were precise but not accurate. \\  \\ \\ \\  \\ \\
\\ 
Sincerely, \\
Henry V. Gilbert. \\ \\ 
x \\ \\ 
Enclosed: Thin-walled pressure vessel report. 





% ================. Executive Summary  ====================
\newpage
\section*{Executive Summary} 



% ================. Table of Contents ====================
\newpage
\tableofcontents




% ================.List of Figures  ====================
\newpage
\listoffigures


% ================. Tables  ====================
\newpage
\listoftables

% ================ List of Symbols.  ====================




% ================. Introduction ====================
\newpage
\pagenumbering{roman}
\section{Introduction}
\paragraph{Background}











\end{document}